hbm_paper_results

### 2024-02-07 paper_lbcc_results.Rmd
mostly plots

Sample
```{r}
sample_boxplot <- ggplot(cent_deltas_df, aes(y=reorder(study, -age_years), x=age_years, color=sex)) +
  geom_boxplot(outlier.size = 1, outlier.colour=NULL) +
  theme_linedraw(base_size = 11) +
  labs(color="Sex", x = "Age (Years)", y = "Study")

sample_barplot <- ggplot(cent_deltas_df) +
  geom_bar(aes( x=..count../tapply(..count.., ..y.. ,sum)[..y..], y=reorder(study, -age_years), fill=sex)) + 
  scale_x_continuous(labels = scales::percent) +
  geom_vline(xintercept = .5, color="lightgray", linetype="longdash") +
  theme_linedraw(base_size = 11) +
  theme(axis.ticks.y = element_blank(), axis.text.y=element_blank(), axis.title.y=element_blank()) +
  labs(color="Sex", x = "% Study")

ggarrange(sample_boxplot, sample_barplot, 
          nrow=1, ncol=2, 
          align = "h", 
          common.legend = TRUE,
          widths=c(2, 1))
```

@@

age_effects.plt <- delta_sum.df_piv %>%
  ggplot(aes(x=mean_age_yrs, y=(study_mean_abs.delta*100))) +
  geom_count(aes(size=study_n, color=sex_prop_Female)) +
  paletteer::scale_color_paletteer_c("grDevices::Oslo", name = "Proportion \nFemale") +
  geom_smooth(method="lm", color="#060B14FF") +
  theme_linedraw(base_size = 11) +
  labs(size="Study N", x = "Mean Age (Years)", y = "Mean Absolute Difference in Centile Scores")
```

@@

sex_effects.plt <- delta_sum.df_piv %>%
  ggplot(aes(x=sex_prop_Female, y=(study_mean_delta*100))) +
  geom_count(aes(size=study_n, color=mean_age_yrs)) +
  geom_smooth(method="lm", color="#006027FF") +
  paletteer::scale_color_paletteer_c("grDevices::Greens 2", name = "Mean Age \n(Years)") +
  theme_linedraw(base_size = 11) +
  labs(size="Study N", x = "Proportion Female", y = "Mean Difference in Centile Scores")

@@

#Regional
regional.delta_plt <- cent_delta_lms.df_toplt %>%
  dplyr::filter(pheno_cat != "Global Volume") %>%
  mutate(estimate = case_when(sig_fdr == FALSE ~ NA,
                                     TRUE ~ estimate*100)) %>%
  ggplot() +
  theme_linedraw(base_size=12) +
  ggseg::geom_brain(atlas = dk_nomed, 
             position = position_brain(hemi ~ side),
             aes(fill = estimate)) +
  facet_grid(term ~ pheno_cat, labeller = labeller(term = as_labeller(term_names))) + 
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=2/3, plot.margin = margin(1,1,1,1, 'pt'), strip.text.y = element_blank()) +
  paletteer::scale_fill_paletteer_c("grDevices::Cork", name = "Beta", limits = c(-0.1, 0.1))

#Global
global.delta_plt <- cent_delta_lms.df_toplt %>%
  dplyr::filter(pheno_cat == "Global Volume") %>%
  mutate(estimate = case_when(sig_fdr == FALSE ~ NA,
                                     TRUE ~ estimate*100),
         tissue_class = as.factor(case_when(pheno == "GMV" ~ "cGM",
                                            pheno == "Ventricles" ~ "CSF",
                                            pheno == "WMV" ~ "WM",
                                            pheno == "sGMV" ~ "sGM",
                                            TRUE ~ NA))) %>%
  dplyr::select(!any_of(c("label", "region", "hemi"))) %>% #drop cols corresponding to dk regions
  ggplot() +
  theme_linedraw(base_size=12) +
  ggseg::geom_brain(atlas = aseg_cerebrum, 
             side = c("coronal"),
             aes(fill = estimate)) +
  facet_grid(term ~ pheno_cat, labeller = labeller(term = as_labeller(term_names)), switch = 'y') + 
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=2/3, plot.margin = margin(1,1,1,1, 'pt')) +
  paletteer::scale_fill_paletteer_c("grDevices::Cork", name = "Beta", limits = c(-0.1, 0.1))
```

@@

```{r}
# study demographics
fig4 <- ggarrange(
  ggarrange(
ggarrange(sample_boxplot, sample_barplot,
          nrow=1, ncol=2, 
          align = "h", 
          common.legend = TRUE,
          legend="bottom",
          widths=c(2, 1)),

@@

fig4_annotate <- annotate_figure(fig4, top = text_grob("Figure 4. Differences in centile scores of lifespan consortium data when harmonized with ComBat-GAM and ComBatLS", color = "black", hjust = 0, x = 0))
fig4_annotate
ggsave("figs/figure_4.jpeg", fig4_annotate, width=12, height=10, units="in")
```

>>>>

Sample
```{r}
sample_boxplot <- ggplot(cent_deltas_df, aes(y=reorder(study, -age_years), x=age_years, color=sex)) +
  geom_boxplot(outlier.size = 1, outlier.colour=NULL) +
  theme_linedraw(base_size = 11) +
  theme(axis.title.x=element_blank(), axis.text.x=element_blank()) +
  labs(color="Sex", y = "Study")

#overall sample
full_boxplot <- 
  cent_deltas_df %>%
  mutate(ylab = "   Full Sample") %>%
  ggplot(aes(y=ylab, x=age_years, color=sex)) +
  geom_boxplot(outlier.size = 1, outlier.colour=NULL) +
  theme_linedraw(base_size = 11) +
  # theme(plot.margin = margin(0,0,0,0, 'cm')) +
  # scale_y_discrete(labels=c("1" = "Full Sample")) +
  labs(color="Sex", x = "Age (Years)", y="")

sample_barplot <- ggplot(cent_deltas_df) +
  geom_bar(aes( x=..count../tapply(..count.., ..y.. ,sum)[..y..], y=reorder(study, -age_years), fill=sex)) + 
  scale_x_continuous(labels = scales::percent) +
  geom_vline(xintercept = .5, color="lightgray", linetype="longdash") +
  theme_linedraw(base_size = 11) +
  theme(axis.ticks.y = element_blank(), axis.text=element_blank(), axis.title=element_blank()) +
  labs(color="Sex")

full_barplot <- 
  cent_deltas_df %>%
  mutate(ylab = "Full Sample") %>%
  ggplot() +
  geom_bar(aes(x=..count../tapply(..count.., ..y.. ,sum)[..y..], y=ylab, fill=sex)) + 
  scale_x_continuous(labels = scales::percent) +
  geom_vline(xintercept = .5, color="lightgray", linetype="longdash") +
  theme_linedraw(base_size = 11) +
  theme(axis.ticks.y = element_blank(), axis.text.y=element_blank(), axis.title.y=element_blank()) +
  labs(color="Sex", x = "Sex")

ggarrange(sample_boxplot, sample_barplot,
          full_boxplot, full_barplot,
          nrow=2, ncol=2, 
          align = "hv", 
          common.legend = TRUE,
          widths=c(2, 1),
          heights=c(10, 1))
```

@@

age_effects.plt <- delta_sum.df_piv %>%
  ggplot(aes(x=mean_age_yrs, y=(study_mean_abs.delta*100))) +
  geom_count(aes(size=study_n, color=sex_prop_Female)) +
  paletteer::scale_color_paletteer_c("ggthemes::Blue", name = "Proportion \nFemale") +
  geom_smooth(method="lm", color="#2A5783FF") +
  theme_linedraw(base_size = 11) +
  labs(size="Study N", x = "Mean Age (Years)", y = "Mean Absolute Difference in Centile Scores")
```

@@

sex_effects.plt <- delta_sum.df_piv %>%
  ggplot(aes(x=sex_prop_Female, y=(study_mean_delta*100))) +
  geom_count(aes(size=study_n, color=mean_age_yrs)) +
  geom_smooth(method="lm", color="#24693DFF") +
  paletteer::scale_color_paletteer_c("ggthemes::Green", name = "Mean Age \n(Years)") +
  theme_linedraw(base_size = 11) +
  labs(size="Study N", x = "Proportion Female", y = "Mean Difference in Centile Scores")

@@

#Regional
regional.delta_plt <- cent_delta_lms.df_toplt %>%
  dplyr::filter(pheno_cat != "Global Volume") %>%
  mutate(estimate = case_when(sig_fdr == FALSE ~ NA,
                                     TRUE ~ estimate*100)) %>%
  ggplot() +
  theme_linedraw(base_size=12) +
  ggseg::geom_brain(atlas = dk_nomed, 
             position = position_brain(hemi ~ side),
             aes(fill = estimate)) +
  facet_grid(term ~ pheno_cat, labeller = labeller(term = as_labeller(term_names))) + 
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=2/3, plot.margin = margin(1,1,1,1, 'pt'), strip.text.y = element_blank()) +
  paletteer::scale_fill_paletteer_c("grDevices::Cork", name = "Beta", limits = c(-0.11, 0.11), breaks=c(-0.1, 0, 0.1))

#Global
global.delta_plt <- cent_delta_lms.df_toplt %>%
  dplyr::filter(pheno_cat == "Global Volume") %>%
  mutate(estimate = case_when(sig_fdr == FALSE ~ NA,
                                     TRUE ~ estimate*100),
         tissue_class = as.factor(case_when(pheno == "GMV" ~ "cGM",
                                            pheno == "Ventricles" ~ "CSF",
                                            pheno == "WMV" ~ "WM",
                                            pheno == "sGMV" ~ "sGM",
                                            TRUE ~ NA))) %>%
  dplyr::select(!any_of(c("label", "region", "hemi"))) %>% #drop cols corresponding to dk regions
  ggplot() +
  theme_linedraw(base_size=12) +
  ggseg::geom_brain(atlas = aseg_cerebrum, 
             side = c("coronal"),
             aes(fill = estimate)) +
  facet_grid(term ~ pheno_cat, labeller = labeller(term = as_labeller(term_names)), switch = 'y') + 
  theme(axis.title = element_blank(), axis.text = element_blank(), axis.ticks = element_blank(), panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(color= "gray", fill = NA), aspect.ratio=2/3, plot.margin = margin(1,1,1,1, 'pt')) +
  paletteer::scale_fill_paletteer_c("grDevices::Cork", name = "Beta", limits = c(-0.11, 0.11), breaks=c(-0.1, 0, 0.1))
```

@@

```{r}
# study demographics
fig5 <- ggarrange(
  ggarrange(
ggarrange(sample_boxplot, sample_barplot,
          full_boxplot, full_barplot,
          nrow=2, ncol=2, 
          # align = "hv", 
          common.legend = TRUE,
          legend = "bottom",
          widths=c(2, 1),
          heights=c(6, 1)),

@@

fig5_annotate <- annotate_figure(fig5, top = text_grob("Figure 5. Differences in centile scores of lifespan consortium data when harmonized with ComBat-GAM and ComBatLS", color = "black", hjust = 0, x = 0))
fig5_annotate
ggsave("figs/figure_5.jpeg", fig5_annotate, width=12, height=10, units="in")
```

### 2024-02-07 paper_main_results.Rmd
mostly plots

```{r}
dataset_names <- c(ukb_CN = "Raw Data", cf = "ComBat w/o Covar", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")
addline_format <- function(x,...){
    gsub('\\s','\n',x)
}

>>>>

```{r}
dataset_names <- c(ukb_CN = "Raw Data", cf = "ComBat w/o Covar", cf.lm = "ComBat", cf.gam ="ComBat-GAM", cf.gamlss ="ComBatLS")
